---
title: "COVID-19 and Sleep Quality Classification"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidymodels)
library(ranger)
tidymodels_prefer()
```

## Data import

Place the original workbook at `data/SleepAllData.xlsx`.

```{r}
set.seed(1821)

data_path <- file.path("data", "SleepAllData.xlsx")
if (!file.exists(data_path)) {
  stop("Missing data/SleepAllData.xlsx. See data/README.md for the expected file.")
}

sleep_raw <- read_excel(data_path) %>%
  select(-any_of(c("Q19", "Q32", "Q10", "Q11")))

required_columns <- c("Q15", "Q26", "Q27")
missing_required <- setdiff(required_columns, names(sleep_raw))
if (length(missing_required) > 0) {
  stop("Missing required columns: ", paste(missing_required, collapse = ", "))
}
```

## Deterministic feature engineering

BMI is calculated from the source height/weight fields using the original project definition. Rows with missing target values are excluded. A row-level completeness filter is applied before splitting because it depends only on each row's own observed values, not on distribution estimates learned from other observations.

```{r}
sleep_data <- sleep_raw %>%
  mutate(
    BMI = if_else(
      !is.na(Q26) & !is.na(Q27) & Q27 > 0,
      round(Q26 / (Q27^2), 1),
      NA_real_
    ),
    Group_BMI = case_when(
      BMI < 18.5 ~ "Underweight",
      BMI < 25 ~ "HealthyWeight",
      BMI < 30 ~ "Overweight",
      BMI >= 30 ~ "Obese",
      TRUE ~ NA_character_
    ),
    Q15 = factor(
      Q15,
      levels = c(3, 2, 1, 0),
      labels = c("VeryBad", "Bad", "Good", "VeryGood")
    )
  ) %>%
  filter(!is.na(Q15)) %>%
  filter(rowMeans(!is.na(.)) > 0.95) %>%
  mutate(across(where(is.character), factor))

table(sleep_data$Q15)
```

## Stratified train/test split

The split occurs before near-zero-variance filtering, imputation or any other learned preprocessing.

```{r}
set.seed(1821)
sleep_split <- initial_split(sleep_data, prop = 0.75, strata = Q15)
sleep_train <- training(sleep_split)
sleep_test <- testing(sleep_split)
```

## Leakage-safe preprocessing recipe

The recipe is estimated separately inside every resample during tuning. The held-out test set is never used to determine near-zero-variance columns or imputation values.

```{r}
sleep_recipe <- recipe(Q15 ~ ., data = sleep_train) %>%
  step_nzv(all_predictors()) %>%
  step_unknown(all_nominal_predictors(), new_level = "unknown") %>%
  step_novel(all_nominal_predictors(), new_level = "new") %>%
  step_impute_median(all_numeric_predictors()) %>%
  step_impute_mode(all_nominal_predictors())
```

## Ranger Random Forest

```{r}
rf_spec <- rand_forest(
  trees = 1000,
  mtry = tune(),
  min_n = tune()
) %>%
  set_engine("ranger", importance = "permutation") %>%
  set_mode("classification")

rf_workflow <- workflow() %>%
  add_recipe(sleep_recipe) %>%
  add_model(rf_spec)

set.seed(1821)
folds <- vfold_cv(sleep_train, v = 5, strata = Q15)

rf_parameters <- extract_parameter_set_dials(rf_workflow) %>%
  finalize(sleep_train)

set.seed(1821)
rf_grid <- grid_space_filling(rf_parameters, size = 15)

set.seed(1821)
rf_tuning <- tune_grid(
  rf_workflow,
  resamples = folds,
  grid = rf_grid,
  metrics = metric_set(accuracy, kap)
)

collect_metrics(rf_tuning)
```

## Final held-out evaluation

The best hyperparameters are chosen from training resamples only. `last_fit()` then fits the complete workflow on the training partition and evaluates once on the untouched test partition.

```{r}
best_rf <- select_best(rf_tuning, metric = "accuracy")
final_workflow <- finalize_workflow(rf_workflow, best_rf)

set.seed(1821)
final_fit <- last_fit(
  final_workflow,
  split = sleep_split,
  metrics = metric_set(accuracy, kap)
)

collect_metrics(final_fit)
```

```{r}
heldout_predictions <- collect_predictions(final_fit)
conf_mat(heldout_predictions, truth = Q15, estimate = .pred_class)
```

## Why the legacy workflow is archived

The original exploratory analysis fitted K-nearest-neighbour imputation separately on the test set, calculated some filtering/outlier decisions before the split and indexed Ranger tuning results with an `mtry` value as though it were a row number. It also labelled the square root of Ranger's classification error as RMSE. Those choices are not used in this audited workflow.

SMOTE and AVF experimentation are intentionally omitted from the baseline. They can be reintroduced later only inside training resamples, where they cannot influence the held-out set.

## Scope

This is an academic machine-learning project. It is not a sleep-disorder diagnostic tool and its results should not be used for clinical decisions.

## Session information

```{r}
sessionInfo()
```
